---
title: "Linear Analysis"
author: "Insight"
date: "24/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}

cat("\014")    # to clear console to CTRL+L
rm(list=ls())  
library(dplyr)
library (readr)



data<-read.csv(url("https://raw.githubusercontent.com/imi-insight/InSession/master/Linear%20Regression/Datasets/multipleChoiceResponses.csv"))

schema=read.csv(url("https://raw.githubusercontent.com/imi-insight/InSession/master/Linear%20Regression/Datasets/schema.csv"))
schema
names(schema)
levels(as.factor(schema$Asked))
library(sqldf)
```

```{r}

col=data.frame(sqldf("Select Column from schema where Asked = 'All'"))
col_all=col[,1]
col_all
library(dplyr)
```

```{r}

cols=c("GenderSelect","Country","Age","EmploymentStatus","StudentStatus",
       "LearningDataScience","CodeWriter","CareerSwitcher",
       "CurrentJobTitleSelect","CurrentEmployerType","MLToolNextYearSelect",
       "MLMethodNextYearSelect","LanguageRecommendationSelect","PublicDatasetsSelect","LearningPlatformSelect",
       "LearningPlatformUsefulnessArxiv","LearningPlatformUsefulnessBlogs","LearningPlatformUsefulnessCollege",
       "LearningPlatformUsefulnessCompany","LearningPlatformUsefulnessConferences","LearningPlatformUsefulnessFriends",
       "LearningPlatformUsefulnessKaggle","LearningPlatformUsefulnessNewsletters","LearningPlatformUsefulnessCommunities",
       "LearningPlatformUsefulnessDocumentation","LearningPlatformUsefulnessCourses","LearningPlatformUsefulnessProjects",
       "LearningPlatformUsefulnessPodcasts","LearningPlatformUsefulnessSO","LearningPlatformUsefulnessTextbook",
       "LearningPlatformUsefulnessTradeBook","LearningPlatformUsefulnessTutoring","LearningPlatformUsefulnessYouTube",
       "BlogsPodcastsNewslettersSelect","LearningDataScienceTime","JobSkillImportanceBigData","JobSkillImportanceDegree",
       "JobSkillImportanceStats","JobSkillImportanceEnterpriseTools","JobSkillImportancePython","JobSkillImportanceR",
       "JobSkillImportanceSQL","JobSkillImportanceKaggleRanking","JobSkillImportanceMOOC","JobSkillImportanceVisualizations",
       "HardwarePersonalProjectsSelect","TimeSpentStudying","ProveKnowledgeSelect","DataScienceIdentitySelect",
       "FormalEducation","MajorSelect","Tenure","PastJobTitlesSelect","FirstTrainingSelect","LearningCategorySelftTaught",
       "LearningCategoryOnlineCourses","LearningCategoryWork","LearningCategoryUniversity","LearningCategoryKaggle",
       "MLSkillsSelect","MLTechniquesSelect","ParentsEducation","EmployerIndustry","EmployerSize","EmployerSizeChange",
       "EmployerMLTime","EmployerSearchMethod","UniversityImportance","JobFunctionSelect","WorkHardwareSelect",
       "WorkDataTypeSelect","WorkProductionFrequency","WorkDatasetSize","WorkAlgorithmsSelect","WorkToolsSelect",
       "WorkToolsFrequencyAmazonML","WorkToolsFrequencyAWS","WorkToolsFrequencyAngoss","WorkToolsFrequencyC","WorkToolsFrequencyCloudera",
       "WorkToolsFrequencyDataRobot","WorkToolsFrequencyFlume","WorkToolsFrequencyGCP","WorkToolsFrequencyHadoop","WorkToolsFrequencyIBMCognos",
       "WorkToolsFrequencyIBMSPSSModeler","WorkToolsFrequencyIBMSPSSStatistics","WorkToolsFrequencyIBMWatson","WorkToolsFrequencyImpala",
       "WorkToolsFrequencyJava","WorkToolsFrequencyJulia","WorkToolsFrequencyJupyter","WorkToolsFrequencyKNIMECommercial","WorkToolsFrequencyKNIMEFree",
       "WorkToolsFrequencyMathematica","WorkToolsFrequencyMATLAB","WorkToolsFrequencyAzure","WorkToolsFrequencyExcel",
       "WorkToolsFrequencyMicrosoftRServer","WorkToolsFrequencyMicrosoftSQL","WorkToolsFrequencyMinitab","WorkToolsFrequencyNoSQL",
       "WorkToolsFrequencyOracle","WorkToolsFrequencyOrange","WorkToolsFrequencyPerl","WorkToolsFrequencyPython",
       "WorkToolsFrequencyQlik","WorkToolsFrequencyR","WorkToolsFrequencyRapidMinerCommercial","WorkToolsFrequencyRapidMinerFree",
       "WorkToolsFrequencySalfrod","WorkToolsFrequencySAPBusinessObjects","WorkToolsFrequencySASBase","WorkToolsFrequencySASEnterprise",
       "WorkToolsFrequencySASJMP","WorkToolsFrequencySpark","WorkToolsFrequencySQL","WorkToolsFrequencyStan",
       "WorkToolsFrequencyStatistica","WorkToolsFrequencyTableau","WorkToolsFrequencyTensorFlow","WorkToolsFrequencyTIBCO",
       "WorkToolsFrequencyUnix","WorkMethodsSelect","WorkMethodsFrequencyAssociationRules",
       "WorkMethodsFrequencyBayesian","WorkMethodsFrequencyCNNs","WorkMethodsFrequencyCollaborativeFiltering",
       "WorkMethodsFrequencyDataVisualization","WorkMethodsFrequencyDecisionTrees",
       "WorkMethodsFrequencyEnsembleMethods","WorkMethodsFrequencyEvolutionaryApproaches","WorkMethodsFrequencyGANs","WorkMethodsFrequencyGBM","WorkMethodsFrequencyHMMs",
       "WorkMethodsFrequencyKNN","WorkMethodsFrequencyLiftAnalysis","WorkMethodsFrequencyLogisticRegression","WorkMethodsFrequencyMLN","WorkMethodsFrequencyNaiveBayes",
       "WorkMethodsFrequencyNLP","WorkMethodsFrequencyNeuralNetworks","WorkMethodsFrequencyPCA","WorkMethodsFrequencyPrescriptiveModeling",
       "WorkMethodsFrequencyRandomForests","WorkMethodsFrequencyRecommenderSystems","WorkMethodsFrequencyRNNs",
       "WorkMethodsFrequencySegmentation","WorkMethodsFrequencySimulation","WorkMethodsFrequencySVMs","WorkMethodsFrequencyTextAnalysis",
       "WorkMethodsFrequencyTimeSeriesAnalysis","WorkMethodsFrequencySelect1","WorkMethodsFrequencySelect2","WorkMethodsFrequencySelect3",
       "TimeGatheringData","TimeModelBuilding","TimeProduction","TimeVisualizing","TimeFindingInsights",
       "AlgorithmUnderstandingLevel","WorkChallengesSelect","WorkChallengeFrequencyDeployment","CompensationAmount","CompensationCurrency")

useful_df=data %>% select(cols)
```

```{r}
write.csv(useful_df,"kaggleSalData.csv")
sum(!is.na(useful_df$CompensationAmount))
#install.packages("naniar")
library(naniar)   
useful_df <- useful_df %>% dplyr::na_if("")
df=useful_df[!is.na(useful_df$CompensationAmount),]
df = subset(df, select = -c(WorkMethodsFrequencySelect1,WorkMethodsFrequencySelect2,WorkMethodsFrequencySelect3,WorkToolsFrequencyMathematica) )
df = subset(df, select = -c(WorkMethodsFrequencyLiftAnalysis,WorkMethodsFrequencyHMMs,WorkMethodsFrequencyGANs) )
summary(df)